CS246 Progress Report: Twitter Purifier

### 2014-05-07 Progress Report.tex
string -> word

We observe the squeezing phenomenon quite often on Twitter, e.g. \textit{I am soooooo happy!}, \textit{it's gooooooooooood}. Usually, people use this to express their emotions or to emphasize particular words. We developed a rule-based filter to ``clean'' such squeezed words based on the letter being duplicated. In our algorithm, we generate a candidate list for all possible original words since there are cases with multiple possible original words. For example, we can find tweets \textit{Oh my goooooooooood!} and \textit{it's gooooooooooooood}. In such a situation, we cannot distinguish between ``god" or ``good" by looking at the original string, so we leave all possibilities in the candidate correction list. The module for this has been completed.

>>>>

We observe the squeezing phenomenon quite often on Twitter, e.g. \textit{I am soooooo happy!}, \textit{it's gooooooooooood}. Usually, people use this to express their emotions or to emphasize particular words. We developed a rule-based filter to ``clean'' such squeezed words based on the letter being duplicated. In our algorithm, we generate a candidate list for all possible original words since there are cases with multiple possible original words. For example, we can find tweets \textit{Oh my goooooooooood!} and \textit{it's gooooooooooooood}. In such a situation, we cannot distinguish between ``god" or ``good" by looking at the original word, so we leave all possibilities in the candidate correction list. The module for this has been completed.
